\mytitle

### 2023-06-08 expanded-paper.tex
Improved expand.js help text
Trying to get Elsevier's Latex processing to work

\received{30 April 2022}
\revised{8 June 2022, 3 January 2023, 31 January 2023 \& 12~May~2023} 
\volumenumber{00} \issuenumber{0} \volumeyear{2023}

@@

%\section*{Author summary}
%
%%\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{HT}}]
%Harold Thimbleby PhD, FRCP (Edinburgh), Hon.\ FRSA, Hon.\ FRCP is See Change Fellow in Digital Health at Swansea University, Wales. His research focuses on human error and computer system design, particularly for healthcare. 
%%In addition to over 340 peer-reviewed and 188 invited publications, Harold has written several books, including \emph{Press On\/} (MIT Press, 2007), which was winner of the American Association of Publishers best book in computer science award.
%Harold won the British Computer Society Wilkes Medal. He is emeritus Gresham Professor of Geometry (a chair founded in 1597), and has been a Royal Society-Leverhulme Trust Senior Research Fellow and a Royal Society-Wolfson Research Merit Award holder. His latest book is  \emph{Fix IT: How to see and solve the problems of digital healthcare\/} \cite{fixit}.  See his web site, \texttt{www.harold.thimbleby.net}, for more details.

%\noindent\emph{This paper evidences widespread problems arising from scientific papers relying on inadequately defined computer and inaccessible code, which undermines peer-review and replication, and undermines scientific quality generally. The risks vary, depending on how critical a paper's claims may be: ranging from superficial for opinion papers, to serious for papers in domains such as medicine, public health, or policy. This paper contrasts the situation with the mature approach to using statistics, and goes on to make proposals to help address the problem. The proposals are feasible, and presented in the hope of motivating their (or better solutions) being implemented, tested, and refined.}

@@

\begin{figure\figureStarDetails}[t]
{ \newdimen \imageWidth 
  \imageWidth=\textwidth
  \imageWidthCalculation
  \begin{center}\includegraphics[width=\imageWidth]{
generated/mathematicaplot.jpg
}\end{center}}
\caption{Much computational science is concerned with finding plausible multi-dimensional models that fit models to data with the aim of extrapolating or predicting new results from them. Shown here is notional sample of experimental 2D data (the dots), a linear least squares regression, and an exact polynomial model. The over-fitted polynomial model fits the sample \emph{exactly\/}, but since the experimental data is presumably subject to random error (indicated by the confidence interval, itself estimated) the linear model would generally be considered a better description of the experimental data.}
\label{fig-overfit}
\end{figure\figureStarDetails}

@@

%An example is the documentation at the code repository \xcite{BayesWaveCode}, which requires three high-profile \emph{{Physics Review D}} papers \xcite{BayesWave1,BayesWave2,BayesWave3} be cited to acknowledge any use, but only one of them, \xcite{BayesWave3}, mentions the code, and even then it fails to acknowledge the contributions of its 10 programmers (despite 6 being co-authors). The paper does cite the repository URL, but unlike the papers it cites conventionally, it omits all the code's authors. Acknowledgement does not seem to matter, even to the people who did the work.

@@

In reaction to this vicious cycle, there is a growing movement to use and cite code correctly \cite{cite-code,TOP}, because code \emph{is\/} important, particularly for the reproduction, testing, and extension of any scientific work. (Code also needs to be correct, not just cited correctly.)

%Few journals editorial policies recognize that data and code are theoretically and in practice indistinguishable (see \supplement). Given that data and code are equivalent and interchangeable, it follows that publishing policies on data handling should also apply at least as strictly to code.

@@

%Since the symmetries in the scientific domains should be reflected in corresponding symmetries in well-designed code, this raises new possibilities of Formal Methods approaches (e.g., using automatic theorem provers) supporting advances in general science.

\section{State of the art}% \\ in computational science}

@@

\subsection{The paper as a scientific laboratory}\label{paper-as-lab}
The conventional view of science is that experiments are done \emph{then\/} written up. 
%RAP and \RAPstar\ support and enhance this process with computational tools; in particular, the archival results of research are not just the reports and publications, but include the executable processes --- the pipelines in RAP terms --- of the research. 
However, it is more productive to think of the paper itself as an active laboratory, not just as a record of finished work. The view of the paper as a scientific laboratory is explicit in computational papers (section \ref{computable-papers}): ideas are written down, and their validity is tested by the sense they make or fail to make; the ideas are then revised --- writing is an active experiment to find and develop ideas that are worth saying. Viewing the paper as a laboratory encourages authors to copy and adopt laboratory best practice (such as keeping records, as RAP and \RAPstar\ suggest) into the processes of writing the paper itself; viewing the paper as a laboratory also encourages authors to see writing as a scientifically --- not just expressive --- act, and not just as the final summary of a period of scientific creativity. In short, seen as a laboratory, the paper is no longer a reactive write-up of finished work, but it is an active part of doing good science. Writing a paper explores the space of scientific possibility as constructively as working in the field or on a lab bench. The computable paper is now the scientific laboratory.

>>>>

\received{30 April 2022}
\revised{8 June 2022, 3 January 2023, 31 January 2023, 12~May~2023 \& 7~June~2023} 
\volumenumber{00} \issuenumber{0} \volumeyear{2023}

@@

@@

\begin{figure\figureStarDetails}[t]
{ \newdimen \imageWidth 
  \imageWidth=\textwidth
  \imageWidthCalculation
  \begin{center}%
% removed generated/ from graphics pathname
\includegraphics[width=\imageWidth]{expanded-plot.\imageFileSuffix}
\end{center}}
\caption{Much computational science is concerned with finding plausible multi-dimensional models that fit models to data with the aim of extrapolating or predicting new results from them. Shown here is notional sample of experimental 2D data (the dots), a linear least squares regression, and an exact polynomial model. The over-fitted polynomial model fits the sample \emph{exactly\/}, but since the experimental data is presumably subject to random error (indicated by the confidence interval, itself estimated) the linear model would generally be considered a better description of the experimental data.}
\label{fig-overfit}
\end{figure\figureStarDetails}

@@

@@

In reaction to this vicious cycle, there is a growing movement to use and cite code correctly \cite{cite-code,TOP}, because code \emph{is\/} important, particularly for the reproduction, testing, and extension of any scientific work. (Code also needs to be correct, not just cited correctly.) Few journals editorial policies recognize that data and code are in practice indistinguishable (see \supplement). Given that data and code are equally important in science, effectively equivalent and interchangeable, it follows that publishing policies on data handling should also apply at least as strictly to code.

@@

\section{State of the art}

@@

\subsection{The paper as a scientific laboratory}\label{paper-as-lab}
The conventional view of science is that experiments are done \emph{then\/} written up. However, it is more productive to think of the paper itself as an active laboratory, not just as a record of finished work. The view of the paper as a scientific laboratory is explicit in computational papers (section \ref{computable-papers}): ideas are written down, and their validity is tested by the sense they make or fail to make; the ideas are then revised --- writing is an active experiment to find and develop ideas that are worth saying. Viewing the paper as a laboratory encourages authors to copy and adopt laboratory best practice (such as keeping records, as RAP and \RAPstar\ suggest) into the processes of writing the paper itself; viewing the paper as a laboratory also encourages authors to see writing as a scientifically --- not just expressive --- act, and not just as the final summary of a period of scientific creativity. In short, seen as a laboratory, the paper is no longer a reactive write-up of finished work, but it is an active part of doing good science. Writing a paper explores the space of scientific possibility as constructively as working in the field or on a lab bench. The computable paper is now the scientific laboratory.
